ABC inferences

### 2024-12-16 extensive_tests/abc_inferences/draft-abc-inferences-vignette.Rmd
Updating environment.yaml

@@

@@

@@

Requires the following packages (already included in environment.yaml):
```{r, eval = FALSE}
install.packages("BiocManager")
BiocManager::install("Biostrings")
```

@@

```{r}
# Filter the data for the given chromosome and region
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start > dpp4_start - 5e5 & CpG_count$start < dpp4_end + 5e5, ]

@@

>>>>

# Workflow dependencies

Are listed under the file `environment.yaml`. Before running the workflow, a conda environment can be created with:

```{bash, eval = FALSE}
conda env create -n abc_inferences -f environment.yaml
```

@@

Add info on how to download the reference genome from progress report.

@@

Both under subdirectory genomic_dist

@@

@@

```{r}
# Filter the data for the given chromosome and region
filtered_data <- CpG_count[CpG_count$chr == dpp4_chr & CpG_count$start >= dpp4_start - 5e5 & CpG_count$start <= dpp4_end + 5e5, ]

@@

X-axis corresponds to the positions in chromosome `r dpp4_chr`
dpp4_start
dpp4_end
